Precise spiking motifs in neurobiological and neuromorphic data

### 2022-12-19 manuscript.tex
in sync

%%----------------------------%
\remove[LP]{
\begin{figure}
\centering
\includegraphics[width=\linewidth]{figures/pcbi.1006283.g001.png}%pcbi.1006283.g001.PNG_L.png}
\caption{\textbf{The SPOTDisClust algorithm.} Fig 1 of~\citep{grossberger_unsupervised_2018}, showing simulated example illustrating the steps in the algorihtm. \textbf{(A)} Structure of five ``ground-truth'' patterns (\ldots). For each pattern and each neuron, a random position was chosen for the activation pulse. \textbf{(B)} Neuronal output is generated according to an inhomogeneous Poisson process, with rates dictated by the patterns in (A). (© Authors under a \href{https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1006283}{CC licence})}\label{fig:SPOTDisClust}
\end{figure}
%----------------------------%
}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scaling up to very large scale data}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Over the past decade, tremendous technological advances across several disciplines have dramatically expanded the frontiers of experimentally accessible neuroscientific facts. Bridging across different spatial and temporal scales, combination of \textit{in vivo} two photon imaging, large population recording-array technologies, optogenetic circuit control tools, transgenic manipulations as well as large volume circuit reconstructions are now used to examine the function, structure and dynamics of neural networks on an unprecedented level of detail and precision. The daunting complexity of the biological reality revealed by these technologies highlights the importance of neurobiological knowledge to provide a conceptual bridge between abstract principles of brain function and their biological implementations within neural circuits. As a consequence, there is a growing need to scale these methods to larger amounts of data.

>>>>

% %%----------------------------%
% \remove[LP]{
% \begin{figure}
% \centering
% \includegraphics[width=\linewidth]{figures/pcbi.1006283.g001.png}%pcbi.1006283.g001.PNG_L.png}
% \caption{\textbf{The SPOTDisClust algorithm.} Fig 1 of~\citep{grossberger_unsupervised_2018}, showing simulated example illustrating the steps in the algorihtm. \textbf{(A)} Structure of five ``ground-truth'' patterns (\ldots). For each pattern and each neuron, a random position was chosen for the activation pulse. \textbf{(B)} Neuronal output is generated according to an inhomogeneous Poisson process, with rates dictated by the patterns in (A). (© Authors under a \href{https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1006283}{CC licence})}\label{fig:SPOTDisClust}
% \end{figure}
% %----------------------------%
% }
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scaling up to very large scale data}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Over the past decade, tremendous technological advances across several disciplines have dramatically expanded the frontiers of experimentally accessible neuroscientific facts. Bridging across different spatial and temporal scales, combination of \textit{in vivo} two photon imaging, large population recording-array technologies, optogenetic circuit control tools, transgenic manipulations as well as large volume circuit reconstructions are now used to examine the function, structure and dynamics of neural networks on an unprecedented level of detail and precision. The daunting complexity of the biological reality revealed by these technologies highlights the importance of neurobiological knowledge to provide a conceptual bridge between abstract principles of brain function and their biological implementations within neural circuits. As a consequence, there is a growing need to scale these methods to larger amounts of data.
